---
title: "Panel Data Analysis: Price Markdown Effects on Retail Sales"
subtitle: Data provided by PricewaterhouseCoopers Japan
author: Rivaldo Philip
date: "`r format(Sys.time(), '%B %d, %Y')`"
#font-import:
  #font-family: 'Yantramanav'
output:
  html_document:
    number_sections: no
    self_contained: yes
keywords: machine learning; econometrics; panel data
theme: null
editor_options:
  chunk_output_type: inline
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, comment=NA)
```

```{r results='hide',message=FALSE}
library(readr)
library(tidyverse)
library(magrittr)
library(dplyr)
library(seasonal)
library(urca)
library(dynlm)
library(CausalImpact)
library(arsenal)
library(phtt)
library(foreign)
library(fastDummies)
library(Hmisc)
library(dynlm)
library(plm)
library(forecast)
library(panelView) 
library(data.table)
```

```{r echo=FALSE, results='hide',message=FALSE}
# Preparing the dataframe
# PwC_data <- read_csv("Datasets/PwC Hackathon/PwC data.csv")
# PwC_data$type <- NULL
# na_count <-sapply(pwc_panel, function(y) sum(length(which(is.na(y)))))
# na_count <- data.frame(na_count)
# 
# storedum <- dummy_cols(PwC_data$store)
# 
# PwC_panel <- cbind(PwC_data, storedum)
# PwC_panel$store <- NULL
# 
# write.csv(PwC_panel, "Datasets/PwC Hackathon/PwC panel data.csv")
pwc_panel <- read_csv("Datasets/PwC Hackathon/PwC panel data.csv")
pwc_panel$date <- as.Date(pwc_panel$date, "%m/%d/%Y")
pwc_panel %<>% mutate_at(c(2,5,16:60), as.factor)

# combine store and dept as id
pwc_seq <- pwc_panel
pwc_seq$id <- paste(pwc_seq$store, "-", pwc_seq$dept)
pwc_seq <- pwc_seq[,c(61,1:60)]
pwc_seq <- pwc_seq[-c(2:3)]

pwc_seq <- pdata.frame(pwc_seq, c("id", "date"))

all(is.pconsecutive(pwc_seq))
```

```{r results='hide', message=FALSE}
# Create First Differences
pwc_seq %<>%
  mutate(lag_wsales = Hmisc::Lag(wsales,1)) %>%
  mutate(dwsales = (wsales/lag_wsales)-1)

pwc_seq %<>%
  mutate(lag_unemp = Hmisc::Lag(unemp,1)) %>%
  mutate(dunemp = (unemp/lag_unemp)-1)

pwc_seq %<>%
  mutate(lag_temp = Hmisc::Lag(temp,1)) %>%
  mutate(dtemp = (temp/lag_temp)-1)

pwc_seq %<>%
  mutate(lag_fuel = Hmisc::Lag(fuel,1)) %>%
  mutate(dfuel = (fuel/lag_fuel)-1)

pwc_seq %<>%
  mutate(lag_cpi = Hmisc::Lag(cpi,1)) %>%
  mutate(dcpi = (cpi/lag_cpi)-1)

pwc_seq %<>%
  mutate(lag_md1 = Hmisc::Lag(md1,1)) %>%
  mutate(dmd1 = (md1/lag_md1)-1)

pwc_seq %<>%
  mutate(lag_md2 = Hmisc::Lag(md2,1)) %>%
  mutate(dmd2 = (md2/lag_md2)-1)

pwc_seq %<>%
  mutate(lag_md3 = Hmisc::Lag(md3,1)) %>%
  mutate(dmd3 = (md3/lag_md3)-1)

pwc_seq %<>%
  mutate(lag_md4 = Hmisc::Lag(md4,1)) %>%
  mutate(dmd4 = (md4/lag_md4)-1)

pwc_seq %<>%
  mutate(lag_md5 = Hmisc::Lag(md5,1)) %>%
  mutate(dmd5 = (md5/lag_md5)-1)
```


```{r echo=FALSE, results='hide',message=FALSE}
#Data preparation 2

is.nan.data.frame <- function(x)
do.call(cbind, lapply(x, is.nan))
pwc_seq[is.nan(pwc_seq)] <- 0

pwc_clean<-na.omit(pwc_seq)

pwc_inf <- data.table(pwc_clean)
invisible(lapply(names(pwc_inf),function(.name) set(pwc_inf, which(is.infinite(pwc_inf[[.name]])), j = .name,value =NA)))
pwc_clean2 <- na.omit(pwc_inf)
pwc_clean2 <- pdata.frame(pwc_clean2, c("id", "date"))
```

```{r echo=FALSE}
#Data Structure

head(pwc_clean2)
```

```{r echo=FALSE, results='hide',message=FALSE}
#unit root test
# dept <−data.frame(split(pwc_panel, pwc_panel$dept))
# pwc_purtest<-pdata.frame(pwc_purtest,index=c("dept","date"))
# 
# purtest(wsales~trend,data = pwc_clean2, index = c("id","date"), test = c("levinlin",
#   "ips", "madwu", "Pm", "invnormal", "logit", "hadri"), lags = c("SIC", "AIC", "Hall"), pmax = 4)

# pwc_seq <- pwc_seq %>% ungroup()
```

```{r echo = FALSE}
panelView(wsales ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Weekly Sales", type = "outcome", id = c("1 - 1"))

panelView(dwsales ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Weekly Sales", type = "outcome", id = c("1 - 1"))
```

```{r echo = FALSE}
panelView(cpi ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "CPI", type = "outcome", id = c("1 - 1"))

panelView(dcpi ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD CPI", type = "outcome", id = c("1 - 1"))
```

```{r echo = FALSE}
panelView(unemp ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Unemployment", type = "outcome", id = c("1 - 1"))

panelView(dunemp ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Unemployment", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(temp ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Temperature", type = "outcome", id = c("1 - 1"))

panelView(dtemp ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Temperature", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(fuel ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Fuel", type = "outcome", id = c("1 - 1"))

panelView(dfuel ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Fuel", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(md1 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Discount 1", type = "outcome", id = c("1 - 1"))

panelView(dmd1 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Discount 1", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(md2 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Discount 2", type = "outcome", id = c("1 - 1"))

panelView(dmd2 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Discount 2", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(md3 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Discount 3", type = "outcome", id = c("1 - 1"))

panelView(dmd3 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Discount 3", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(md4 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Discount 4", type = "outcome", id = c("1 - 1"))

panelView(dmd4 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Discount 4", type = "outcome", id = c("1 - 1"))
```

```{r echo=FALSE}
panelView(md5 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "Discount 5", type = "outcome", id = c("1 - 1"))

panelView(dmd5 ~ 1, data = pwc_clean2, index = c("id", "date"), 
          main = "FD Discount 5", type = "outcome", id = c("1 - 1"))
```


```{r}
# Panel data with random effects

random <- plm(dwsales~holiday+dtemp+dfuel+dmd1+dmd2+dmd3+dmd4+dmd5+dcpi+dunemp+size, data=pwc_clean2, model="random", random.method="walhus",index=c("id","date"))
summary(random)
```

```{r}
# Panel data with two-way fixed effects (no store entity fixed effects)

reg <- plm(dwsales~-1+dmd1+dmd2+dmd3+dmd4+dmd5,data=pwc_clean2, model="within", effect="twoways", index=c("id","date"))
summary(reg)
```



```{r}
# Panel data with two-way fixed effects

fixed <- plm(dwsales~ -1+holiday+dtemp+dfuel+dmd1+dmd2+dmd3+dmd4+dmd5+dcpi+dunemp+size+store1+store2+store3+store4+store5+store6+store7+store8+store9+store10+store11+store12+store13+store14+store15+store16+store17+store18+store19+store20+store21+store22+store23+store24+store25+store26+store27+store28+store29+store30+store31+store32+store33+store34+store35+store36+store37+store38+store39+store40+store41+store42+store43+store44+store45, data=pwc_clean2, model="within", effect="twoways", index=c("id","date"))
summary(fixed)
pdwtest(fixed)

fixed2 <- plm(dwsales~ -1+holiday+dtemp+dfuel+plm:::lagt.pseries(dmd1,1)+plm:::lagt.pseries(dmd2,1)+plm:::lagt.pseries(dmd3,1)+plm:::lagt.pseries(dmd3,1)+plm:::lagt.pseries(dmd4,1)+dmd1+dmd2+dmd3+dmd4+dmd5+dcpi+dunemp+size+store1+store2+store3+store4+store5+store6+store7+store8+store9+store10+store11+store12+store13+store14+store15+store16+store17+store18+store19+store20+store21+store22+store23+store24+store25+store26+store27+store28+store29+store30+store31+store32+store33+store34+store35+store36+store37+store38+store39+store40+store41+store42+store43+store44+store45, data=pwc_clean2, model="within", effect="twoways", index=c("id","date"))
summary(fixed2)
pdwtest(fixed2)

fixed3 <- plm(dwsales~ -1+holiday+dtemp+dfuel+plm:::lagt.pseries(dmd1,1)+plm:::lagt.pseries(dmd2,1)+plm:::lagt.pseries(dmd3,1)+plm:::lagt.pseries(dmd3,1)+plm:::lagt.pseries(dmd4,1)+plm:::lagt.pseries(dmd1,2)+plm:::lagt.pseries(dmd2,2)+plm:::lagt.pseries(dmd3,2)+plm:::lagt.pseries(dmd4,2)+dmd1+dmd2+dmd3+dmd4+dmd5+dcpi+dunemp+size+store1+store2+store3+store4+store5+store6+store7+store8+store9+store10+store11+store12+store13+store14+store15+store16+store17+store18+store19+store20+store21+store22+store23+store24+store25+store26+store27+store28+store29+store30+store31+store32+store33+store34+store35+store36+store37+store38+store39+store40+store41+store42+store43+store44+store45, data=pwc_clean2, model="within", effect="twoways", index=c("id","date"))
summary(fixed3)
pdwtest(fixed3)
```

```{r echo=FALSE, results='hide',message=FALSE}
# rasea <- as.data.frame(table(pwc_clean2$id))
# rasea <- as.data.frame(table(rasea$Freq))
# plot(rasea)
# 
# rasea2 <- as.data.frame(table(pwc_phtt2$id))
# rasea2 <- as.data.frame(table(rasea2$Freq))
# plot(rasea2)
# 
# length(unique(pwc_phtt$id))
# length(unique(pwc_phtt2$id))
# length(unique(pwc_phtt3$id))
# length(unique(pwc_phtt4$id))
# 
# rasea4 <- as.data.frame(table(pwc_phtt3$id))
# rasea4 <- as.data.frame(table(rasea4$Freq))
# plot(rasea4)
# 
# rasea5 <- as.data.frame(table(pwc_phtt4$id))
# rasea5 <- as.data.frame(table(rasea5$Freq))
# plot(rasea5)
# 
# rasea3 <- as.data.frame(table(pwc_clean2$size))
```

```{r results='hide',message=FALSE}
# PHTT Setup 1
pwc_phtt <- pwc_clean2
pwc_phtt %<>% group_by(id) %>%
  filter(n() > 130) 
pwc_phtt %<>% mutate_at(c(3:79), as.numeric)

N <- 2215  #depts within stores
T <- 130 #dates

m.dwsales <- matrix(pwc_phtt$dwsales, T, N)
m.md1 <- matrix(pwc_phtt$md1, T, N)
m.md2 <- matrix(pwc_phtt$md2, T, N)
m.md3 <- matrix(pwc_phtt$md3, T, N)
m.md4 <- matrix(pwc_phtt$md4, T, N)
m.md5 <- matrix(pwc_phtt$md5, T, N)
m.dfuel <- matrix(pwc_phtt$dfuel, T, N)
m.dtemp <- matrix(pwc_phtt$dtemp, T, N)
m.dcpi <- matrix(pwc_phtt$dcpi, T, N)
m.dunemp <- matrix(pwc_phtt$dunemp, T, N)
m.holiday <- matrix(pwc_phtt$holiday, T, N)
m.size <- matrix(pwc_phtt$size, T, N)
```


```{r}
# Panel Data PCA mixed stores
pwc_pca<-pwc_phtt[-c(1,2)]
pwc_pca<-data.matrix(pwc_pca)
phtt::OptDim(pwc_pca, d.max=70, criteria = c("IC1", "IC2", "IC3",
                                                   "PC1", "PC2", "PC3"))
```

```{r results='hide',message=FALSE}
# PHTT Setup Only Largest Stores
pwc_phtt2 <- pwc_clean2
pwc_phtt2 %<>% group_by(size) %>%
  filter(size >200000) 
pwc_phtt2 <-ungroup(pwc_phtt2)
pwc_phtt2 %<>% group_by(id)
pwc_phtt2 %<>% mutate_at(c(3:79), as.numeric)

N <- 1009  #depts within stores
T <- 134 #dates

m2.dwsales <- matrix(pwc_phtt2$dwsales, T, N)
m2.md1 <- matrix(pwc_phtt2$md1, T, N)
m2.md2 <- matrix(pwc_phtt2$md2, T, N)
m2.md3 <- matrix(pwc_phtt2$md3, T, N)
m2.md4 <- matrix(pwc_phtt2$md4, T, N)
m2.md5 <- matrix(pwc_phtt2$md5, T, N)
m2.dfuel <- matrix(pwc_phtt2$dfuel, T, N)
m2.dtemp <- matrix(pwc_phtt2$dtemp, T, N)
m2.dcpi <- matrix(pwc_phtt2$dcpi, T, N)
m2.dunemp <- matrix(pwc_phtt2$dunemp, T, N)
m2.holiday <- matrix(pwc_phtt2$holiday, T, N)
m2.size <- matrix(pwc_phtt2$size, T, N)
```


```{r}
# Panel Data PCA large stores
pwc_pca2<-pwc_phtt2[-c(1,2)]
pwc_pca2<-data.matrix(pwc_pca2)
phtt::OptDim(pwc_pca2, d.max=50, criteria = c("IC1", "IC2", "IC3",
                                                   "PC1", "PC2", "PC3"))
```

```{r results='hide',message=FALSE}
# PHTT Setup Only Small Stores
pwc_phtt3 <- pwc_clean2
pwc_phtt3 %<>% group_by(size) %>%
  filter(size <100000) 
pwc_phtt3 <-ungroup(pwc_phtt3)
pwc_phtt3 %<>% group_by(id)
pwc_phtt3 %<>% mutate_at(c(3:79), as.numeric)

N <- 943  #depts within stores
T <- 120 #dates

m3.dwsales <- matrix(pwc_phtt3$dwsales, T, N)
m3.md1 <- matrix(pwc_phtt3$md1, T, N)
m3.md2 <- matrix(pwc_phtt3$md2, T, N)
m3.md3 <- matrix(pwc_phtt3$md3, T, N)
m3.md4 <- matrix(pwc_phtt3$md4, T, N)
m3.md5 <- matrix(pwc_phtt3$md5, T, N)
m3.dfuel <- matrix(pwc_phtt3$dfuel, T, N)
m3.dtemp <- matrix(pwc_phtt3$dtemp, T, N)
m3.dcpi <- matrix(pwc_phtt3$dcpi, T, N)
m3.dunemp <- matrix(pwc_phtt3$dunemp, T, N)
m3.holiday <- matrix(pwc_phtt3$holiday, T, N)
m3.size <- matrix(pwc_phtt3$size, T, N)
```


```{r}
# Panel Data PCA small stores
pwc_pca3<-pwc_phtt3[-c(1,2)]
pwc_pca3<-data.matrix(pwc_pca3)
phtt::OptDim(pwc_pca3, d.max=50, criteria = c("IC1", "IC2", "IC3",
                                                   "PC1", "PC2", "PC3"))
```

```{r results='hide',message=FALSE}
# PHTT Setup Only Medium Stores
pwc_phtt4 <- pwc_clean2
pwc_phtt4 %<>% group_by(size) %>%
  filter(between(size, 100000, 200000))
pwc_phtt4 <-ungroup(pwc_phtt4)
pwc_phtt4 %<>% group_by(id)
pwc_phtt4 %<>% mutate_at(c(3:79), as.numeric)

N <- 1372  #depts within stores
T <- 127 #dates

m4.dwsales <- matrix(pwc_phtt4$dwsales, T, N)
m4.md1 <- matrix(pwc_phtt4$md1, T, N)
m4.md2 <- matrix(pwc_phtt4$md2, T, N)
m4.md3 <- matrix(pwc_phtt4$md3, T, N)
m4.md4 <- matrix(pwc_phtt4$md4, T, N)
m4.md5 <- matrix(pwc_phtt4$md5, T, N)
m4.dfuel <- matrix(pwc_phtt4$dfuel, T, N)
m4.dtemp <- matrix(pwc_phtt4$dtemp, T, N)
m4.dcpi <- matrix(pwc_phtt4$dcpi, T, N)
m4.dunemp <- matrix(pwc_phtt4$dunemp, T, N)
m4.holiday <- matrix(pwc_phtt4$holiday, T, N)
m4.size <- matrix(pwc_phtt4$size, T, N)
```

```{r}
# Panel Data PCA medium stores
pwc_pca4<-pwc_phtt4[-c(1,2)]
pwc_pca4<-data.matrix(pwc_pca4)
phtt::OptDim(pwc_pca4, d.max=50, criteria = c("IC1", "IC2", "IC3",
                                                   "PC1", "PC2", "PC3"))
```

```{r}
# Panel data with interactive fixed effects
interactive <- phtt::Eup(m.dwsales ~ -1 + m.md1+m.md2+m.md3+m.md4+m.md5, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=64, max.iteration=500)
summary(interactive)

interactive2 <- phtt::Eup(m.dwsales~ -1+m.holiday+m.dtemp+m.dfuel+m.md1+m.md2+m.md3+m.md4+m.md5+m.dcpi+m.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=64, max.iteration=500)
summary(interactive2)
```


```{r}
# Panel data with interactive fixed effects for large stores
interactive_large <- phtt::Eup(m2.dwsales ~ -1 + m2.md1+m2.md2+m2.md3+m2.md4+m2.md5, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=43, max.iteration=500)
summary(interactive_large)

interactive_large2 <- phtt::Eup(m2.dwsales~ -1+m2.holiday+m2.dtemp+m2.dfuel+m2.md1+m2.md2+m2.md3+m2.md4+m2.md5+m2.dcpi+m2.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=43, max.iteration=500)
summary(interactive_large2)
```

```{r}
# Panel data with interactive fixed effects for small stores
interactive_small <- phtt::Eup(m3.dwsales ~ -1 + m3.md1+m3.md2+m3.md3+m3.md4+m3.md5, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=45, max.iteration=500)
summary(interactive_small)

interactive_small2 <- phtt::Eup(m3.dwsales~ -1+m3.holiday+m3.dtemp+m3.dfuel+m3.md1+m3.md2+m3.md3+m3.md4+m3.md5+m3.dcpi+m3.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=45, max.iteration=500)
summary(interactive_small2)
```

```{r}
# Panel data with interactive fixed effects for medium stores
interactive_med <- phtt::Eup(m4.dwsales ~ -1 + m4.md1+m4.md2+m4.md3+m4.md4+m4.md5, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=48, max.iteration=500)
summary(interactive_med)

interactive_med2 <- phtt::Eup(m4.dwsales~ -1+m4.holiday+m4.dtemp+m4.dfuel+m4.md1+m4.md2+m4.md3+m4.md4+m4.md5+m4.dcpi+m4.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=48, max.iteration=500)
summary(interactive_med2)
```

```{r}
#Panel setup with wsales lag
pwc_phtt5 <-pwc_phtt
pwc_phtt5 %<>%
  mutate(lag_wsales2 = Hmisc::Lag(lag_wsales,1)) %>%
  mutate(dwsales2 = (lag_wsales/lag_wsales2)-1)

is.nan.data.frame <- function(x)
do.call(cbind, lapply(x, is.nan))
pwc_phtt5[is.nan(pwc_phtt5)] <- 0

pwc_phtt5<-na.omit(pwc_phtt5)

pwc_inf2 <- data.table(pwc_phtt5)
invisible(lapply(names(pwc_inf2),function(.name) set(pwc_inf2, which(is.infinite(pwc_inf2[[.name]])), j = .name,value =NA)))
pwc_phtt5 <- na.omit(pwc_inf2)
pwc_phtt5 <- pdata.frame(pwc_phtt5, c("id", "date"))
```


```{r results='hide',message=FALSE}
# Panel setup with lags
pwc_phtt5 %<>% group_by(id) %>%
  filter(n() > 130) 
pwc_phtt5 %<>% mutate_at(c(3:79), as.numeric)

N <- 2215  #depts within stores
T <- 130 #dates

m.dwsales <- matrix(pwc_phtt5$dwsales, T, N)
m.dwsales2 <- matrix(pwc_phtt5$dwsales2, T, N)
m.md1 <- matrix(pwc_phtt5$md1, T, N)
m.md2 <- matrix(pwc_phtt5$md2, T, N)
m.md3 <- matrix(pwc_phtt5$md3, T, N)
m.md4 <- matrix(pwc_phtt5$md4, T, N)
m.md5 <- matrix(pwc_phtt5$md5, T, N)
m.lmd1 <- matrix(pwc_phtt5$lag_md1, T, N)
m.lmd2 <- matrix(pwc_phtt5$lag_md2, T, N)
m.lmd3 <- matrix(pwc_phtt5$lag_md3, T, N)
m.lmd4 <- matrix(pwc_phtt5$lag_md4, T, N)
m.lmd5 <- matrix(pwc_phtt5$lag_md5, T, N)
m.dfuel <- matrix(pwc_phtt5$dfuel, T, N)
m.dtemp <- matrix(pwc_phtt5$dtemp, T, N)
m.dcpi <- matrix(pwc_phtt5$dcpi, T, N)
m.dunemp <- matrix(pwc_phtt5$dunemp, T, N)
m.holiday <- matrix(pwc_phtt5$holiday, T, N)
m.size <- matrix(pwc_phtt5$size, T, N)
```


```{r}
# Panel data with interactive fixed effects with lags

interactive3 <- phtt::Eup(m.dwsales2~ -1+m.dtemp+m.dfuel+m.lmd1+m.lmd2+m.lmd3+m.lmd4+m.lmd5+m.dcpi+m.dunemp+m.holiday, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=64, max.iteration=500)
summary(interactive3)

interactive4 <- phtt::Eup(m.dwsales2~ -1+m.dtemp+m.dfuel+m.md1+m.md2+m.md3+m.md4+m.md5+m.lmd1+m.lmd2+m.lmd3+m.lmd4+m.lmd5+m.dcpi+m.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=64, max.iteration=500)
summary(interactive4)

interactive5 <- phtt::Eup(m.dwsales2~ -1+m.dtemp+m.dfuel+m.md1+m.md2+m.md3+m.md4+m.md5+m.dcpi+m.dunemp, 
               additive.effects = c("twoways"), dim.criterion = c("PC1", "PC2", "PC3", "BIC3","IC1", "IC2" ,
              "IC3", "IPC1", "IPC2", "IPC3"), d.max=64, max.iteration=500)
summary(interactive5)
```


```{r echo=FALSE, results='hide',message=FALSE}
# Bonus: Forecasting
# e <- tsCV(pwc_11, forecastfunction = naive, h = 4)
# mse <- mean(e^2, na.rm=TRUE)
```


```{r echo=FALSE, results='hide',message=FALSE}
# Bonus: Predicting Counterfactuals using CausalImpact
# time.points <- seq.Date(as.Date("2010-02-12"), by = 14, length.out = 500)
# pwc_11 <- subset(pwc_clean2, id == "1 - 1")
# pwc_11 <- zoo(cbind(pwc_11), time.points)

# pwc_11 <- pwc_11[,c(3,7)]
# pwc_11 <- as.data.frame(pwc_11)
# pwc_11 %<>% mutate_at(c(1,2), as.numeric)
 
# pre.period <- as.Date(c("2010-02-12", "2011-11-04"))
# post.period <- as.Date(c("2011-11-11", "2012-10-26"))
# impact <- CausalImpact(pwc_11, pre.period, post.period)

# summary(impact, "report")
```

```{r echo=FALSE, results='hide',message=FALSE}
# plot(impact)
```

## Challenges
1. Unbalanced panel data
2. Gaps in time series

## Conclusion
The effect of price markdown is not seen in the model. Nevertheless, this may be related to the quality of the data that we have. Some of the data in the markdown are believed to be missing, as there is a very low likelihood that the stores did not conduct any markdowns for an entire year.

## Further Research
Formal unit root test, determination of lags, forecasting, and causal inference, if we are able to gather more balanced data without missing values or gaps.
